\documentclass[letterpaper,10pt,titlepage]{article}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
%\usepackage[TABBOTCAP, tight]{subfloat}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

%random comment

%\include{pygments.tex}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}



\def\name{Neale Ratzlaff}
\title{Motivation for Master's Degree in Computer Science}

\author{Neale Ratzlaff}
\date{14 April 2016}

\let\endtitlepage\relax

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {CS472},
  pdftitle = {CS 472 Assignment 1},
  pdfsubject = {CS 472 Project 1},
  pdfpagemode = UseNone
}

\begin{document}
\maketitle


    &Through my undergraduate studies in ECE I found difficulty in being interested in any area of study, and never imagined continuing my studies in a graduate program. This reflected onto my GPA as I struggled to be interested in ECE. 
    Six months into my third year, technical excellence became vital as I discovered machine learning and computer vision, fields that I knew I wanted to persue because of the potential and depth I see in them.
    I believe the study of Machine learning and AI is at the heart of man's drive to understand his place in the world, causing inorganic matter to have perceptions, intuitions, and decisions has shown us how much we do, and do not understand intelligence.  
    Dispite my formal studies being in electrical and computer engineering, I absorbed the literature from every possible source and took on every project where I could apply machine learning. 
    My most rewarding experience was patenting a classifier I developed during one of my internships. I've had the pleasure of having many mentors who were instumental in making me into a better engineer and leader, I have them to thank for the confidance in engineering I have now.
    I now have the experience of leading multiple teams over the course of this last year, one working on computer vision, another developing autopilot systems for drones. 
    My experience with machine learning and computer vision has given me a love and excitement for the theory, and a drive to work among those who have dedicated their lives to the field. I wish to replace my early undergraduate acedemic record with a focused and motivated graduate career.
    A graduate program will not only allow me to work with generative models, computational geometry, and deep learning, topics that are inaccessible to an undergraduate, but also to learn about them from researchers.
    The last two years at Oregon State have taught me what I am capable of, and also about the level of expertise that can follow a dedicated student. Because of the growth I have seen in my abilities, both as an engineer and leader, I know that I can be a valueble asset if given the chance to learn.  
    The overwhelming lesson I have learned through studying the field of AI is how far the road stretches ahead. The weight of the journey is daunting and exciting, I want to learn eveything I can and also give back to the field that gave me passion in engineering. 

\end{document}
