\documentclass[letterpaper,10pt,titlepage]{article}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
%\usepackage[TABBOTCAP, tight]{subfloat}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

%random comment

%\include{pygments.tex}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfpagemode = UseNone
}



\def\name{Neale Ratzlaff}
\date{14 April 2016}

\begin{document}
\section{Motivation for Master's Degree in Computer Science}
    \author{Neale Ratzlaff}

    Through my undergraduate studies in ECE I found difficulty in being interested in any area of study, and never imagined continuing my studies in grad school. This reflected onto my GPA as I struggled to be interested in ECE. 
    6 months into my third year, technical excellence became vital as I discovered machine learning and computer vision, fields that I knew I wanted to persue. 
    Dispite my formal studies being in electrical and computer engineering, I absorbed the literature from every possible source and took on every project where I could apply machine learning. 
    My most rewarding experience was patenting a classifier I developed during one of my internships. I've had the pleasure of mentors who were instumental in making me into a leader.
    I now have the experience of leading multiple teams over the course of this last year, one team working on computer vision, another developing autopilot systems for drones. 
    My experience with machine learning and computer vision has given me a love and excitement for the theory, and a drive to work among those who have dedicated their lives to the field. I wish to replace my early undergraduate acedemic record with a focused and motivated graduate career.
  
\end{document}
